Classify veg

### 2021-02-25 R/classify_species.Rmd
added boolean variable to train or load classifier

@@

```{r caret_parallel, eval=FALSE}
start.time = Sys.time()

@@

```{r plot_mtry_tuning, eval=FALSE}
# load mtry tuning model
model <- readRDS("output/model_mtry_tuning.rds")

@@

```{r optimize_ntree, eval=FALSE}
# https://rpubs.com/phamdinhkhanh/389752

@@

```{r ntree_tuning_results, eval=FALSE}
# load ntree tuning model list
modellist <- readRDS("output/modelList_ntree_tuning.rds")

@@

```{r randomForest_species_train, eval=FALSE}
set.seed(44)

@@

```{r randomForest_train_confMatrix, fig.width=14, fig.height=14, message=FALSE, eval=FALSE}
# list all combinations of true and predicted species 
all_combos <- expand.grid(obs = unique(rf_train_results$obs), 
				    pred = unique(rf_train_results$obs))

@@

```{r randomForest_train_genus, eval=FALSE}
set.seed(44) # for obama

>>>>

```{r run_or_read_models}

# TRUE or FALSE
# TRUE = train and tune the classification model 
# or FALSE =  read existing files, do not train a new model each time.
run_models <- TRUE
```

@@

```{r caret_parallel, eval=run_models}
start.time = Sys.time()

@@

```{r plot_mtry_tuning, eval=run_models}
# load mtry tuning model
model <- readRDS("output/model_mtry_tuning.rds")

@@

```{r optimize_ntree, eval=run_models}
# https://rpubs.com/phamdinhkhanh/389752

@@

```{r ntree_tuning_results, eval=run_models}
# load ntree tuning model list
modellist <- readRDS("output/modelList_ntree_tuning.rds")

@@

```{r randomForest_species_train, eval=run_models}
set.seed(44)

@@

```{r randomForest_train_confMatrix, fig.width=14, fig.height=14, message=FALSE, eval=run_models}
# list all combinations of true and predicted species 
all_combos <- expand.grid(obs = unique(rf_train_results$obs), 
				    pred = unique(rf_train_results$obs))

@@

```{r randomForest_train_genus, eval=run_models}
set.seed(44) # for obama
